Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex

\begin{table}
\begin{tabular}{ | l | l | l | l | l |}
\hline
Cap Owner & Failure & ZLog Recovery \\ \hline
mds & mds & mds \\ \hline
client & mds & xfer client cap \\ \hline
mds & client & n/a \\ \hline
client & client & mds \\
\hline
\end{tabular}
\caption{Failure and recovery scenarios.}
\label{t:mds-zlog-fail}
\end{table}

>>>>

\begin{table}
\centering
\begin{tabular}{  l | l | l    }
\textbf{Service} & \textbf{Ceph Component} & \textbf{Used for...}  \\ \hline
Mantle  & RADOS    & policy durability \\
        & MON maps & policy versioning \\ \hline
ZLog    & Logical Storage & CORFU protocol  \\ 
        & MON maps & interface install \\ \hline
Seq.    & MDS file types & log management \\ 
        & MDS fault toler. & seq. fault toler. \\
\end{tabular}
\caption{To implement the Mantle and ZLog services, we leverage Ceph components. Malacology uses these subsystems because they provide powerful abstractions.}
\label{table:implementation}
\end{table}

In this section we describe two services built on top of Malacology. The first
is Mantle, a framework for dynamically specifying metadata load balancing
policies. The second system, ZLog, is a high-performance distributed shared-log.
In addition to these services, we'll demonstrate how we combine ZLog and Mantle
to implement service-aware metadata load balancing policies.
